\section{Story and Overview}
    \subsection{Introduction}
        \subsubsection{General Overview}
            It is the year 1942 during the midst of the 2nd world war. 
            A Boeing B-17 Flying Fortress carrying six Allied soldiers crash 
            land onto a mysterious island in the pacific ocean after an attack 
            from a Japanese fighter aircraft. Now they have to defend themselves 
            from the wildlife of the island as well as from the native inhabitants 
            who doesn\textquotesingle t seem very friendly towards the guests until they find a 
            way to escape from the deathly claws of the island.
        \subsubsection{Basic Game Details}
            \paragraph{Genre}\mbox{}\\
                The Island is an adventure based survival game with co-op support. 
            \paragraph{Platform}\mbox{}\\
                The Island will be available on PC and will be limited to Windows 7/8/8.1/10 operating systems. 
            \paragraph{Target Demographic}\mbox{}\\
                Our target audience is between the range of ages 18-35. The game 
                will contain some amount of gore and violence. We aim to hook the 
                players who are interested in co-op gameplay. Co-op gameplay will 
                be completely optional to the players who prefer single play. 
                Additionally the game will feature an adventure based story with 
                survival, which will cater to a wide demographic of users. 
            \paragraph{Perspective}\mbox{}\\
                The game is played from third person perspective.
    \subsection{Plot Points}
        \paragraph{Arrival}\mbox{}\\
            We can see a cinematic of 6 assigned soldiers flying in a Boeing 
            B-17 Flying Fortress above the ocean. They are suddenly attacked 
            from behind by an enemy Japanese Fighter aircraft. James who is piloting 
            the aircraft frantically tries to control it. The aircraft gradually begins descrnding
            despite his best efforts and he suddenly sees an island. James orders the crew
            to jump and try to steer the aircraft towards what seems like somewhat 
            even land covered with a very thick layer of trees. And the plane crashes 
            few seconds after.
        \paragraph{Awakening}\mbox{}\\
            \textbf{James} awakes on the cockpit of the plane. He is having a mild 
            concussion and having a hard time remembering what exactly happened. He 
            realize that the front end of the plane is stuck on a tree high above. He 
            use a vine to get on the ground and then loose conscience. \\
            \textbf{Carter} finds himself hanging in a tree by parachute. He manages
            to cut down his parachute and get to the ground. He then proceeds to search
            for the plane and finds the front half of the aircraft and the unconscious 
            James near it. \\
            \textbf{Cheng} and \textbf{Sally} manages to land in an even ground with their
            parachutes. After a long walk they arrive at the crash site to find their crew
            members sitting in a crate full of weapons near the frontal half of the plane. 
        \paragraph{Burial}\mbox{}\\
            The survivors find the other 2 members of the plane dead. They've had bad luck
            with landing and their bodies were gnawed at by some carnivores roaming the forest. 
            They bury the comrades with saddened hearts. 
        \paragraph{Surviving}\mbox{}\\
            The crew try to survive in the tropical forest. They are having a hard
            time with so many life threatening elements in the forest. 
        \paragraph{Enemies}
            One day when James get lost in the forest and on trying to find his way
            out, he accidentally arrives at the beach of the west side of the island. 
            And he discovers that the island is a secret base for the Axis power.
            German soldiers have camped in the beached and they are moving huge crates 
            of weapons out from the caves.
        \paragraph{Conflict}
            It is inevitable that the patriotic crew getting engaged with the enemy
            soldiers in the other part of the island. Now apart from the usual deathly
            threats in the jungle, they have to fend off enemy soldiers too. 
            After a number of gunfires and bombings at different places, the crew 
            manages to kill most of the Germans in the island. 
        \paragraph{Boss battle}
            Finally the crew manages to catch, Viktor Smirnov, the enemy commander 
            within their submarine. After a long fight, Carter manages to kill him 
            by blowing part of the cabin room. 
        \paragraph{Departure}
            The story ends when the crew finally depart from the island using the
            submarine, to go back to their homelands. 
    \subsection{Environments}
        \subsubsection{Descriptions}
            \begin{itemize}
                \item \textbf{Crash site} - This is the base of the all player operations.
                Debries of the fallen aircraft and some medicine along with weapons can be found
                in this area. Acts as the safe house of the crew.
                \item \textbf{West Beach} - Germans have their base of operations in the west part
                of the island. Player only reaches this region in the latter parts of the game.
                \item \textbf{Submarine} - Boss battle happens in the submarine. Players can't operate
                anything inside the submarine.
                \item \textbf{Forest} - Large part of the game occurs inside the forest in the 
                island. This is a free roaming environment where players have to scavenger for 
                food to survive. 
            \end{itemize}
        % \subsubsection{Concept Art}
    % \subsection{Non Interactive Sequences}
    %     \subsubsection{Descriptions}
    %     \subsubsection{Storyboard}